Using Altruistic Peers to Help With Free Web Downloads

### 2008-03-06 docs/motivation/motivation.tex
Rename project to apt-p2p.

A sample implementation has been created that functions as described
in section \ref{opportunity}. This software, called
\texttt{apt-dht}, interacts with the \texttt{apt} tool found in most
Debian-based Linux distributions. Apt uses SHA1 hashes to
verify most downloaded files, including the large index files that
contain the hashes of the individual packages. We chose this
distribution system as it is familiar to us, and there are
interesting statistics available for analyzing the popularity of the
software packages \cite{popcon}.

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{apt_dht_simulation-size_CDF.eps}
\caption{The CDF of the size of packages in a Debian system, both
for the actual size and adjusted size based on the popularity of
the package.}
\label{size_CDF}
\end{figure}

>>>>

A sample implementation has been created that functions as described
in section \ref{opportunity}. This software, called
\texttt{apt-p2p}, interacts with the \texttt{apt} tool found in most
Debian-based Linux distributions. Apt uses SHA1 hashes to
verify most downloaded files, including the large index files that
contain the hashes of the individual packages. We chose this
distribution system as it is familiar to us, and there are
interesting statistics available for analyzing the popularity of the
software packages \cite{popcon}.

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{apt_p2p_simulation-size_CDF.eps}
\caption{The CDF of the size of packages in a Debian system, both
for the actual size and adjusted size based on the popularity of
the package.}
\label{size_CDF}
\end{figure}
